### 2019-02-21 sections/relatedwork.tex
add citations on HipHop and Esterel

\paragraph{HipHop}

HipHop \fixme{cite} is a programming language tailored to the development synchronous reactive web systems.
From a single source, both server and client applications can be generated.
Programs are written in the Hop language, a Scheme dialect.
Communication is based on a reactive layer embedded in Hop.
Each reactive component starts by specifying possible input and output events.
The component then proceeds as a state machine.

@@

As with \TOPHAT, HipHop is a \DSL embedded in a general purpose programming language.
% the same way \TOPHAT is embedded into the simply typed $\lambda$-calculus.
Another similarity is that both specifications lead to executable server and client applications from a single source.
However, HipHop is more low level regarding its specification.
Where \TOPHAT takes tasks and collaboration as a starting point,
HipHop focusses on synchronous communication and atom execution of reactive machines.

@@

\paragraph{Esterel}

The set of HipHop reactive statements is based on those of the Esterel language.
Esterel is a programming language

>>>>

\paragraph{HipHop \& Esterel}

HipHop \cite{berry2011hiphop} is a programming language tailored to the development synchronous reactive web systems.
From a single source, both server and client applications can be generated.
Programs are written in the Hop language, a Scheme dialect.
Communication is based on a reactive layer embedded in Hop.
The set of HipHop reactive statements is based on those of the Esterel language \cite{boussinot1991esterel}.
Each reactive component starts by specifying possible input and output events.
The component then proceeds as a state machine.

@@

As with \TOPHAT, HipHop is a \DSL embedded in a general purpose programming language.
% the same way \TOPHAT is embedded into the simply typed $\lambda$-calculus.
Another similarity is that both specifications lead to executable server and client applications from a single source.
However, both HipHop and Esterel are more low level regarding their specification.
Where \TOPHAT takes tasks and collaboration as a starting point,
HipHop focusses on synchronous communication and atom execution of reactive machines.

@@
